%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------


\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\color{NavyBlue}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{NavyBlue}\titlerule \vspace{-5pt}]


% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

 
\begin{document}

%----------HEADING----------


\begin{center}
    {\Huge \color{NavyBlue} \textbf {Akash Gupta}} \\ \vspace{1pt}
    \href{mailto:akashgp9@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{akashgp9@gmail.com}} ~ 
    \href{https://github.com/akashgp09}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/akashgp09}} ~
    \href{https://linkedin.com/in/akashgp09}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/akashgp09}} ~
    \small \raisebox{-0.1\height}\faPhone +91 9101225535 

    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Kalinga Institute of Industrial Technology}{June 2019 -- July 2023}
      {Bachelor of Technology in Information Technology CGPA: 9.38/10}{Bhubaneswar, Odisha} 
       \item Relevant Coursework: Data Structures, Algorithms, Operating Systems, DBMS and Computer Networks.
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://summerofcode.withgoogle.com/projects/\#5380240265707520}{Google Summer of Code}}{May 2021 -- August 2021}
      {Student Developer - MetaBrainz Foundation Inc}{Remote}
      \resumeItemListStart
        \resumeItem{Developed a new feature  "Series" entity for  \href{https://bookbrainz.org/}{\textbf{BookBrainz}} used by 2000+ users and added support in BookBrainz \href{https://api.test.bookbrainz.org/1/docs/}{\textbf{API}}.}
        \resumeItem{Designed and created the database schema, Implemented the corresponding ORM models and functions with tests.}
        \resumeItem{Created the web server routes and frontend components.}
        \resumeItem{Increased coverage by 5 percent by adding unit and integration tests using Chai and Mocha framework.}
        \resumeItem{Worked on technologies such as React, Redux, Typescript, Nodejs, PostgreSQL, Bookshelf.js(ORM), and ElasticSearch.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://www.linkedin.com/company/dsckiit/posts/}{Google Developer Students Club, KIIT}}{August 2020 -- Present}
      {Full Stack Web Developer}{Bhubaneswar, Odisha}
      \resumeItemListStart
        \resumeItem{Rebuilt the website from scratch for improved performance and added new features.}
        \resumeItem{Developed the participant web portal for \href{https://dsc-asjx.vercel.app/}{\textbf{ASJX}} - an online hackathon. Integrated Devfolio SDK script for registrations, logging and submissions.}
        \resumeItem{Organized KIIT University's biggest android hackathon.}
        \resumeItem{Worked with different languages, platforms, frameworks, and content management systems such as TypeScript, JavaScript, Next.js, React, Strapi, Material-UI, and Vercel.}
    \resumeItemListEnd
 
    
    \resumeSubheading
      {\href{https://www.elastic.co/community/contributor}{Elastic Contributor Program}}{Feb 2021 -- Present}
      {Contributor}{Remote}
      \resumeItemListStart
        \resumeItem{Helped in the development of  \href{https://eui.elastic.co/}{\textbf{Elastic UI Framework}}, which has over 20k+ downloads per week on npm.}
        \resumeItem{My work includes fixing bugs, adding features, improving documentation, and writing tests.}
        \resumeItem{Automated accessibility testing using AXE and debugged several issues.}
        \resumeItem{Worked with Typescript, React, Jest and a11y.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/akashgp09/coding-platform}{Coding Platform}} $|$ \emph{Javascript, React, MongoDB, Nodejs, Express}}{August 2020}
          \resumeItemListStart
            \resumeItem{Developed a coding portal where people can practice their coding skills.}
            \resumeItem{Integrated a compiler that supports code execution for C, C++, Python, and Java.}
            \resumeItem{Integrated CodeMirror, a versatile text editor for editing code.}
            \resumeItem{Executes code against test cases (default or custom) to measure the correctness of the user's code.}
            \resumeItem{Used Google Oauth authentication strategy for sign-in/sign-up.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{\href{https://github.com/akashgp09/Jammming}{Jammming}} $|$ \emph{React, Spotify API}}{May 2020}
          \resumeItemListStart
            \resumeItem{A web application built with React that allows to search the Spotify library, create a custom playlist, and then save the playlist to their Spotify accounts.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, C, C++, Python, SQL} \\
     \textbf{Development}{: React, TypeScript, Next.js, Node.js, Express, BookShelf.js(ORM), Chai, Mocha} \\
     \textbf{Database}{: MySQL, PostgreSQL, MongoDB} \\
     \textbf{Others}{: Linux, Git, Software Testing, API Development, Problem Solving} \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Additional}

 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Open Source Contributions:}{: Contributed to Layer5, Meshery, Open Collective, Dev Protocol.} \\
     \textbf{Elastic Contributor Program}{: Currently    \textbf{ranked 4} in  East Asia, South Asia, Southeast Asia, and Oceania region leaderboard.} \\
     \textbf{Writing}{: Published multiple technical articles on \href{https://akashgp09.medium.com/}{\textbf{Medium}}.} \\
    }}
 \end{itemize}

\end{document}
